Active Learning Benchmark

### 2023-01-27 doc/research_presentation/research_presentation.tex

\begin{frame}[fragile]{Cross Validation}
	Splice: 
	random 0.874 +- 0.01
	margin 0.885 +- 0.015
	difference 0.011
	Changing the data vs. changing the model initialization
\end{frame}

>>>>

\begin{frame}[fragile]{Cross Validation}
	\begin{columns}
		\begin{column}{0.3\linewidth}
			Splice (Tabular): \\
			Random: $0.874 \pm 0.01$ \\
			Margin: $0.885 \pm 0.015$ \\
			Difference: $0.011$
			%Changing the data vs. changing the model initialization
		\end{column}
		\hspace{3mm}
		\begin{column}{0.7\linewidth}
			\includegraphics[width=0.9\linewidth]{pics/splice_performance.png}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[fragile]{Cross Validation}
	AL can cross validate in two ways
	\begin{itemize}
		\item Changing the seed set
		\item Changing the presented sub-samples of unlabeled points
		\item Changing model initialization
	\end{itemize}
	Currently, I keep the seed set fixed \\ [2mm]
	Is there value in fixing everything? (Model checkpoints, pre-sampling data*, etc.)
\end{frame}
